%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Security System Company (SSC)}  % Organization
    {Full Stack Developer} % Job title
    {Damascus, Syria} % Location
    {May. 2022 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Demonstrated expertise in the development and maintenance of a full featured GPS tracking system encompassing versatile 
        device protocols compatibility.}
        \item {Designed and Implemented REST API endpoints integrated seamlessly with a user-friendly interface, allowing for the display of GPS data in the form of comprehensive reports.}
        \item {Collaborated closely with hardware engineers to guarantee the accurate implementation of device protocols within the system,thereby ensuring accurate parsing of GPS data.}
        \item {Dramatically enhanced system performance when displaying extensive route data on maps by profiling the code-base and minimizing redundant component tree re-renders within the React framework.}
        \item {Effectively deployed and installed the system within dockerized containers on Linux machines leveraging a reverse proxy (Apache) to facilitate data compression and configuring HTTPS connections.}
      \end{cvitems}
    }
    \begin{cventrytechstack}
        \cvtechstack
        {Tech Stack} % Category
        {React,  Redux,  Java,  JAX-RS,  Jetty,  Jersey,  MariaDB,    Docker} % Skills
    \end{cventrytechstack}

%---------------------------------------------------------
  \cventry
    {Miskolc University \headersocialstyle{%
      \ifthenelse{\isundefined{\@github}}%
        {}%
        {%
          {\hspace{10pt}}%
          \href{https://www.mdpi.com/2411-9660/6/2/39}{\faWpforms\acvHeaderIconSep\@Link to publication}%
        }%
        }
        }% Job title
    {Software Engineer \& Researcher} % Organization
    {Hungary (remote)} % Location
    {Dec. 2021 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-authored a scientific paper focusing on the study and implementation of multi-objective constrained optimization, specifically exploring the application of meta-heuristic algorithms in the field of waste management and logistics.}
        \item {Effectively translated our research case study and intricate mathematical constraints into a robust implementation using the Python programming language.}
        \item {Researched, prototyped and implemented various metaheuristic optimization algorithms including Genetic algorithm, Particle Swarm Optimization and Ant Colony Optimization, and customized these algorithms to fit our specific case study.}
        \item {Employed open routing service API to enrich research visuals with Time/Distance and Directions data. Achieved precise algorithmic route visualization, enhancing the waste management system's comprehensive representation.}
      \end{cvitems}
    }


\end{cventries}
